---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
data(EuStockMarkets)
mode(EuStockMarkets)
class(EuStockMarkets)
plot(EuStockMarkets)

#pdf("EuStocks.pdf", width = 6, height = 5)
plot(EuStockMarkets)

logR = diff(log(EuStockMarkets))
plot(logR)

plot(as.data.frame(logR))

par(mfrow=c(2, 2))
for(i in colnames(logR))
{
  print(i)
  qqnorm(logR[ ,i], datax = T, main = i)
  qqline(logR[ ,i], datax = T)
  print(shapiro.test(logR[ ,i]))
}

n=dim(logR)[1]
q_grid=(1:n)/(n+1)
df_grid = c(1, 4, 6, 10, 20, 30)
index.names = dimnames(logR)[[2]]
for(i in 1:4){
  # dev.new() 
  par(mfrow = c(3, 2)) 
  for(df in df_grid){
    qqplot(logR[,i], qt(q_grid,df),
           main = paste(index.names[i], ", df = ", df) )
    abline(lm(qt(c(0.25, 0.75), df = df) ~
                quantile(logR[,i], c(0.25, 0.75))))
  }
}

library("fGarch")
x=seq(-0.1, 0.1,by = 0.001)
par(mfrow = c(1, 1)) 
df=5
mad_t = mad(logR[ , 1],
            constant = sqrt(df / (df - 2)) / qt(0.75, df))
plot(density(logR[ , 1]), lwd = 2, ylim = c(0, 60))
lines(x, dstd(x, mean = mean(logR[,1]), sd = mad_t, nu = df),
      lty = 5, lwd = 2, col = "red")
lines(x, dnorm(x, mean = mean(logR[ ,1]), sd = sd(logR[ ,1])),
      lty = 3, lwd = 4, col = "blue")
legend("topleft", c("KDE", paste("t: df = ",df), "normal"),
       lwd = c(2, 2, 4), lty = c(1, 5, 3),
       col = c("black", "red", "blue"))
```
